%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage[usenames, dvipsnames]{color}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[RE,Lo]{Mohamed Gamal Mohamed Sweelam}
\fancyfoot[LE,RO]{\today}

\newsectionwidth{15pt} % Stops section indenting

\definecolor{gray}{gray}{0.97}
\begin{document}


\pagecolor{gray}
\name{\LARGE Mohamed Sweelam\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Mohamed Gamal Sweelam } \\ 
Email:\color{blue}MohamedSweelam@fci.helwan.edu.eg \\
Date of Birth: 26--2--1993. \\
Mob: (+ 02) 012 714 59 665
} % Your address 1

\address{{\bf Address}  \\
 15 May City, \\
 Helwan--Cairo \\
 \hspace{0.5cm}{Egypt} } % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}


\section{\large \color{blue}CAREER OBJECTIVE}

\vspace{5pt} % Gap between title and text

Build a strong and a highly qualified career as \textbf{ Data Scientist Java-specialized } developer in software programming, development and research, through working in productive and creative team.So that in the future we can create leading \& advanced software solutions. 

\section{\large \color{blue}EDUCATION} 

\vspace{5pt} % Gap between title and text

{\sl Bachelor of Science, Computer Science}, \\
Faculty of Computer and Information Systems, Helwan university \hfill 2011 –- 2015 \\ 
GPA \bf Good
 

\section{\large \color{blue}CERTFIFCATES} 

\vspace{5pt} % Gap between title and text

{\sl Certificate: English Conversation} \hfill July -- December 2011 \\
{\sl Certificate: Human Computer Interaction research lab } \hfill June -- August 2013 \\
{\sl Machine learning Accomplishment Stanford University } \hfill October -- December 2013 \\
{\sl B.CS: Computer Science Helwan University } \hfill June 2015 \\
{\sl Certificate: Project Management } \hfill July -- September 2014

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

\section{\large \color{blue} GRADUATION PROJECT}
\vspace{5pt} % Gap between title and text

Building smart cross platform Data Visualization framework for Data analysts, Computer scientists and Statistician, that enables them to interact with huge data in a smart new interactive techniques,
you can interact with big data sources, even if your machine resources are not high, using smart technique that we developed to make sure that your cpu or gpu could handle with it rendering in a comfortable mode , and your RAM also load the data in a good manner.

\begin{itemize}
\item \textbf{Languages:} \hspace{2.8cm} JavaScript[ D3 \& Angular ] and C++.
\item \textbf{Grade:}    \hspace{3.6cm} Excellent with honor degree.
\item \textbf{Contests Awards:} 
  \begin{enumerate}
    \item 1st Place MIE Contest. \hfill August 2015.
    \item 1st Place IbteCar Contest. \hspace {2cm} @TIEC \hfill December 2015.
  \end{enumerate}
\end{itimize}


\vspace{0.2in} % Some whitespace between sections

\section{\large \color{blue}TOOLS/ENVIRONMENTS} 
\vspace{5pt} % Gap between title and text
 \center {\bf OS : Linux \& Windows }
\begin{itemize} \itemsep -2pt % Reduce space between items
 \item Eclipse \& IntelliJ. \hspace{3.5cm}  JDeveloper. \hspace{3.3cm} Netbeans.
 \item Tomcat Container.        \hspace{2.4cm} Weblogic App Server.   \hspace{1.7cm} Glassfish Server.
 \item Oracle SQL Developer.    \hspace{2cm} MySql Workbench.    \hspace{3cm} Emacs.  
 \item Webstorm \hspace{5.2cm} R Studio \hspace{2.2cm} Vnc, Winscp and Putty.
\end{itemize}

\newpage

\section{\large \color{blue} PROGRAMMING SKILLS}
 \vspace{5pt}
{\sl \textbf{ Java SE } \hfill  Excellent experience }\\
{\sl \textbf{ Java EE } \hfill Very good experience }\\
{\sl \textbf{ C and C++ } \hfill Very Good experience }\\
{\sl \textbf{ SQL \& PL/SQL } \hfill Very good experience }\\
{\sl \textbf{ Javascript [JQuery -- Ajax], HTML5 and CSS } \hfill Very good experience }\\
{\sl \textbf{ R } \hfill Good experience }\\
{\sl \textbf{ \LaTeX } \hfill Very good experience }\\

\vspace{0.2in} % Some whitespace between sections
\section{\large \color{blue}FRAMEWORKS}
\vspace{5pt}
{\sl \textbf{ Application Development Fusion [ADF]}  \hfill Very good experience}\\
{\sl \textbf{ Spring Boot }   \hfill Very good experience}\\
{\sl \textbf{ Hibernate \& JPA }  \hfill  Good Experience }\\
{\sl \textbf{ Java Server Faces [JSF] } \hfill good expreience}\\
{\sl \textbf{ Thymeleaf template engine } \hfill Very good expreience}\\
{\sl \textbf{ AngularJS 1 \& 2 } \hfill Good expreience}\\

\vspace{0.2in}
\section{\large \color{blue}PROJECTS}
\vspace{5pt} % Reduce space between section title and contents
\begin{flushleft}
  {\sl \textbf{ Microfinance system for loan providing. }\hspace{2cm} \href{http://tanmeyah.com}{Tanmeyah} \hfill Java EE {ADF} }\\
  {\sl \textbf{ School bus tracking system. }     \hfill Java EE {Spring Boot} and Thymeleaf }\\
  {\sl \textbf{ City Management System  }         \hfill Java EE {Liferay \& Angularjs 2}\\ 
  {\sl \textbf{ Data Visualization cross platform framework. }\hfill D3.js , Angularjs \& C++ }\\
  {\sl \textbf{ Full ERP system. }\hspace{6cm} \href{http://buducloud.com}{BuduCloud} \hfill Php }\\
  {\sl \textbf{ Meters system for The Egyptian Ministry of Electricity. }\hfill Php \& C++ }\\
\end{flushleft}
 
\vspace{0.2in} % Some whitespace between sections

\section{\large \color{blue} WORK HISTORY}
\vspace{5pt} % Gap between title and text
\begin{flushleft}
 \textit{\color{blue} current} \textbf{\large \color{red} Java Functional Consultant} @Egabi Solution \hfill Aug-2016 \\
Egabi is a globally aspired, yet regionally rooted organization incorporated in Egypt, with expertise in multitude of segments and specialization in a number of areas, possessing an extensive portfolio of products and services carried out by highly skilled professionals.\\

\vspace{0.2in}
\textbf{\large \color{red} Software Engineer} @BuduCloud \hfill Aug 2015 -- Jul-2016  \\

BuduCloud presents top-notch ERP, HR \& CRM Cloud Solutions that are intuitive,
seamless and highly flexible, BuduCloud designs business software solutions aiming to help you manage your business easily and effectively.\\

\vspace{0.2in}
\textbf{\large \color{red}Instructor } @ITSharks \hfill Jun-2015 -- Up to now \\

Instructor of multiple courses at IT Sharks company like Java, C/C++, Data Structure, Object Oriented Design and Algorithms.
\end{flushleft}

\end{resume} 
\end{document}
